Spatial Analysis: Design-Based vs Model-Based

### 2021-01-29 draft.Rnw
added simulation outline

>>>>

__MH Thoughts:__ I'd like to keep this section manageable. Perhaps we start with the following examples \begin{itemize}
  \item simulate via correct model (model outperforms sampling)
   \item simulate via slightly misspecified model (model still outperforms sampling)
  \item simulate via very misspecified model (sampling outperforms model)
  \item simulate via extremely misspecified model (e.g. counts with lots of zeroes and a lot of overdispersion) (neither does well)
\end{itemize}
